Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-27 report/report.tex
Update todo
Improve text connetivity in abstract

\begin{abstract}
Modeling cities in 3D has long been a topic of interest in field of computer graphics.
It is often desirable to recreate real-world cities in 3D applications such as urban design software and video games, and the topic of 3D city reproduction comes with its own set of unique challenges.
So far there have been a lot of research in modelling of 3D road networks, but these projects have often focused on the road networks designated for cars and public transit, and seldom on pedestrian footpaths.
This project assesses the feasibility of reconstructing a city from OpenStreetMap (OSM) road and building data, and will focus on the feasibility of including pedestrian footpaths, by focusing on OSM road and building data in the Stockholm metropolitan area.

An estimate of the positional accuracy of OSM data has been obtained by comparing OSM data to a dataset with a known accuracy.
It was found that the average positional error in the OSM dataset was about 2 meters.
This estimate of the positional error was then used to assess the integrity of the OSM Stockholm road network, by locating critical points where assigning standard widths to the roads would cause collision with other features, and evaluating how many of those points could be eliminated by making ajustments within the found margin of error.
It was found that footpaths were less problematic than other road types (primary, secondary, residential), in terms of feature collisions, and thus should pose no more problems in 3D city reproduction than other road types.
The report concludes with a scientific study of the field of 3D city reproduction. It serves to give an overview of the challenges in the field and place the study and findings of this project in a broader scientific context. 
\end{abstract}

@@

For the purpose of the collision study, each road has been assigned a standard width that is in line with Swedish regulations, since in the OSM dataset, roads are represented as simple polylines, lacking width.
In a 3D representation however, it is crucial that each road object has a spacial width in order to be rendered and seen.
After the width assignment, a program has iterated over all features and calculated how many of them that overlap with any other feature, as well as the total length of the road polylines that is intersecting some other feature.
The program has then calculated how many of these colliding features that can be corrected by making adjustments that are within the positional accuracy of the OSM data (As obtained by the previous study in this report: Assessment of Geodata Precision).

@@

% Monday
% Collision study implementation
    % TODO: Figure detailing the steps in the point-matching algorithm

>>>>

\begin{abstract}
Modeling cities in 3D has long been a topic of interest in field of computer graphics.
It is often desirable to recreate real-world cities in 3D applications such as urban design software and video games, and the topic of 3D city reproduction comes with its own set of unique challenges.
So far there have been a lot of research in modelling of 3D road networks, but these projects have often focused on the road networks designated for cars and public transit, and seldom on pedestrian footpaths.

This project assesses the feasibility of reconstructing a city from OpenStreetMap (OSM) road and building data, and will focus on the feasibility of including pedestrian footpaths, by examining how common it is that these footpaths collide with other map features.
In the collision detection process, the margin of error has been taken as the positional error in the OSM dataset, which has been obtained by comparing OSM data to a dataset with a known accuracy.

It was found that footpaths were less problematic than other road types (primary, secondary, residential), in terms of feature collisions, and thus should pose no more problems in 3D city reproduction than other road types.
The report concludes with a scientific study of the field of 3D city reproduction. It serves to give an overview of the challenges in the field and place the study and findings of this project in a broader scientific context. 
\end{abstract}

@@

The estimate of the positional error has was used to assess the integrity of the OSM Stockholm road network, by locating critical points where assigning standard widths to the roads would cause collision with other features, and evaluating how many of those points could be eliminated by making ajustments within the found margin of error.
For the purpose of the collision study, each road has been assigned a standard width that is in line with Swedish regulations, since in the OSM dataset, roads are represented as simple polylines, lacking width.
In a 3D representation however, it is crucial that each road object has a spacial width in order to be rendered and seen.
After the width assignment, a program has iterated over all features and calculated how many of them that overlap with any other feature, as well as the total length of the road polylines that is intersecting some other feature.
The program has then calculated how many of these colliding features that can be corrected by making adjustments that are within the positional accuracy of the OSM data (As obtained by the previous study in this report: Assessment of Geodata Precision).

@@

% Report, restructuring
% TODO: Improve connectivity between two first paragraphs in the abstract
% TODO: Merge section 3 with the background chapter
% TODO: Move talk about specific geodata to Implementation section
% TODO: Move 4.1 -> Evaluation/Methodology (new section)
% TODO: Overview at the beginning of each chapter
% TODO: Move conclusions to a new Part 2 of Results and Metrics
% TODO: New conclusions and future work section
% TODO: Make research questions even clearer
